A North Sámi to South Sámi machine translation prototype

### 2014-02-07 paper/paper.tex
More
meeting

\setromanfont{Times New Roman}
\setmonofont{FreeMono}

@@

\section{Introduction}
Suggestions from Lene:  
\begin{enumerate}
\item main point: 
\begin{itemize}
\item translation nob-sma which actually is nob-sme-sma (should somehow be in the title?) 
\item the evaluators evaluate nob-sma
\end{itemize}
\item subpoints: 
\begin{itemize}
\item larger syntactic differences between SL an TL than usually done in Apertium?
\item little sma lexical resources, we have to find words by comparing translated texts
\item reaction from sma linguist in the normgiving organ: she sees the possibility of using MT as a help for discussing terminology and getting the best ones into use
\item the language socity is used to the impact from the mojority languages, a new controversial(?) thought is the linguistic impact from another minority lanugage 
\end{itemize}
\end{enumerate}

% Previous work
\cite{tyers09} \cite{wiechetek10} \cite{trosterud12}

\section{Languages}

% [Sámi language area map]

\section{Implementation}

% [Pipeline image]

@@

@@

@@

\section{Evaluation}

\subsection{Statistics}

\begin{table}
  \begin{center}
    \begin{tabular}{|l|r|}
      \hline
      Bilingual dictionary ({\tt sme}$\rightarrow${\tt sma}) & 15,204 \\ % 10776 proper names
      Transfer rules ({\tt sme}$\rightarrow${\tt sma}) & 57 \\
      \hline
    \end{tabular}
    \label{table:transfer}
    \caption{Number of bilingual dictionary entries and transfer rules}
  \end{center}
\end{table}

@@

\subsection{Quantitative}

\subsection{Qualitative}

\subsection{User feedback}

\section{Future work}

\section{Conclusions}

>>>>

\setromanfont{Times New Roman}
%\setmonofont{FreeMono}

@@

\section{Introduction}
%@trond

% Previous work
\cite{tyers09} \cite{wiechetek10} \cite{trosterud12}
% LREC?

%pivot translation references --babych paper

\section{Languages}
%@trond
% [Sámi language area map]

\section{Implementation}
%@fran
% [Pipeline image]

@@

The bilingual dictionary
general dictionary
general words
special domain

\item problems caused by this model: ex from two terms to one term to two terms

Example: nob-1,2   sme-x   sma-1,2

Little nob-sma lexical resources, and total lack of sme-sma, we have to find words by comparing translated texts

@@

\item larger syntactic differences between SL an TL than usually done in Apertium?

@@

\section{Evaluation}
%@ lene,fran
\item translation nob-sma which actually is nob-sme-sma (should somehow be in the title?) 
\item the evaluators evaluate nob-sma

\subsection{Statistics}
%@fran
\begin{table}
  \begin{center}
    \begin{tabular}{|l|r|}
      \hline
      Bilingual dictionary ({\tt sme}$\rightarrow${\tt sma}) & 15,204 \\ % 10776 proper names
      Transfer rules ({\tt sme}$\rightarrow${\tt sma}) & 57 \\
      \hline
    \end{tabular}
    \label{table:transfer}
    \caption{Number of bilingual dictionary entries and transfer rules}
  \end{center}
\end{table}

@@

\subsection{Quantitative}
%@lene
\subsection{Qualitative}
%@lene

\subsection{User feedback}
%@lene

\section{Future work}
%@trond
\section{Conclusions}
%@trond
\item reaction from sma linguist in the normgiving organ: she sees the possibility of using MT as a help for discussing terminology and getting the best ones into use
\item the language socity is used to the impact from the mojority languages, a new controversial(?) thought is the linguistic impact from another minority lanugage
